---
title: "Regression Replication: The Political Economy Consequences of China’s Export Slowdown"
author: "Wei Lu"
output:
  html_document:
    toc: TRUE
---

```{r setup, include=FALSE}
library(readstata13)
library(tidyverse)
library(lfe)
library(stargazer)
knitr::opts_knit$set(root.dir = '/Users/luwei/Dropbox/GDELT/')
knitr::opts_chunk$set(cache=TRUE)
```

Model: $\Delta(Events/L)_{it} = \beta_0(Events/L)_{i, t-1} + \beta ExpShock_{it} + \beta_x X_{it} + D_{prov, t} + D_i + \epsilon_{it}$

Where $X_{it}$ represent additional control variables.

Note that we have verified the stata numbers above, so here we use merged data from stata for regressions directly.

### Table 1

```{r ols}
workfile_data <- as.tibble(read.dta13('CCL_workfile_May29.dta'))
ols_data <- workfile_data %>%
  filter(year>=2013 & year<=2015) %>%
  mutate(prefect_dummy = as.factor(prefect),
         province_year_dummy = as.factor(province_year),
         province_dummy = as.factor(province),
         d_export_cus_pw_i_lag_fiscal_pub_security_pw = d_export_cus_pw*lag_fiscal_pub_security_pw,
         d_export_btkrow_pw00_i_lag_fiscal_pub_security_pw = d_export_btkrow_pw00*lag_fiscal_pub_security_pw,
         d_export_cus_pw_i_share_state_empl2010 = d_export_cus_pw*share_state_empl2010,
         d_export_btkrow_pw00_i_share_state_empl2010 = d_export_btkrow_pw00*share_state_empl2010,
         d_export_cus_pw_i_share_pop_Hukou_2010 = d_export_cus_pw*share_pop_Hukou_2010,
         d_export_btkrow_pw00_i_share_pop_Hukou_2010 = d_export_btkrow_pw00*share_pop_Hukou_2010,
         d_export_cus_pw_i_share_college = d_export_cus_pw*share_college,
         d_export_btkrow_pw00_i_share_college = d_export_btkrow_pw00*share_college,
         d_export_cus_pw_i_lag_investment_pw = d_export_cus_pw*lag_investment_pw,
         d_export_btkrow_pw00_i_lag_investment_pw = d_export_btkrow_pw00*lag_investment_pw,
         )

# lm produces the correct point estimates, but standard errors are off
# Stata's aweights = R's weights in linear regression: https://rstudio-pubs-static.s3.amazonaws.com/279455_1ca98bc2ce5f45ed9ea20a647ef0c4b1.html#analytics_weights_=_glm_weights_param
ols_model_lm <- lm(d_event_pw ~ lag_event_pw + d_export_cus_pw  + prefect_dummy + province_year_dummy,
                   data = ols_data, weights=pop1564_2010)
ols_model_lm$coefficients[1:3]

ols_model <- felm(d_event_pw ~ lag_event_pw + d_export_cus_pw  | prefect + province_year | 0 | province,
                  ols_data, weights=ols_data$pop1564_2010)
```

Build IV models

```{r iv}
iv_fe_iv_group_formula_str <- "| prefect + province_year | (d_export_cus_pw ~ d_export_btkrow_pw00) | province"
row_iv_model <- felm(as.formula(paste("d_event_pw ~ lag_event_pw", iv_fe_iv_group_formula_str)),
                     ols_data, weights=ols_data$pop1564_2010)

controls <- c("dln_Average_wage", "dln_GRP_popCSY", "dln_college_enroll_popCSY")
extra_controls <- c("dln_Mobile_Tel_popCSY", "dln_Internet_Tel_popCSY")
iv_control1_formula_str <- paste("d_event_pw ~ lag_event_pw", paste(controls, collapse=" + "), sep=" + ")
row_iv_control1_model <- felm(as.formula(paste(iv_control1_formula_str, iv_fe_iv_group_formula_str)),
                              ols_data, weights=ols_data$pop1564_2010)

iv_control2_formula_str <- paste(iv_control1_formula_str, paste(extra_controls, collapse=" + "), sep=" + ")
row_iv_control2_model <- felm(as.formula(paste(iv_control2_formula_str, iv_fe_iv_group_formula_str)),
                              ols_data, weights=ols_data$pop1564_2010)

rf_control2_formula_str <- paste(iv_control2_formula_str, "d_export_btkrow_pw00", sep=" + ")
rf_fe_group_formula_str <- "| prefect + province_year | 0 | province"
rf_control2_model <- felm(as.formula(paste(rf_control2_formula_str, rf_fe_group_formula_str)),
                          ols_data, weights=ols_data$pop1564_2010)
```

Produce regression table 1

```{r reg_table_1, results='asis'}
get_first_stage_f <- function(model) round(model$stage1$iv1fstat$d_export_cus_pw['F'])
first_stage_f <- sapply(list(row_iv_model, row_iv_control1_model, row_iv_control2_model), get_first_stage_f)

stargazer(ols_model, row_iv_model, row_iv_control1_model, row_iv_control2_model, rf_control2_model, type='html',
          column.labels = c('OLS', 'IV', 'IV', 'IV', 'RF'),
          dep.var.caption = "Dependent variable: Changes in CLB Events per million",
          dep.var.labels.include = FALSE, omit.stat = c('adj.rsq', 'ser'),
          digits = 4, order = c(2, 8, 9, 1, 3, 4, 5, 6, 7),
          add.lines = list(c('First-stage F-stat', '', first_stage_f)))
```

### Table 2

Build IV models by sector

```{r iv_by_sector}
controls_formula_str <- paste(paste(controls, collapse=" + "), paste(extra_controls, collapse=" + "), sep=" + ")
iv_manuf_model <- felm(as.formula(paste("d_event_manuf_pw ~ lag_event_manuf_pw +",
                                        controls_formula_str, iv_fe_iv_group_formula_str)),
                       ols_data, weights=ols_data$pop1564_2010)
iv_const_model <- felm(as.formula(paste("d_event_const_pw ~ lag_event_const_pw +",
                                        controls_formula_str, iv_fe_iv_group_formula_str)),
                       ols_data, weights=ols_data$pop1564_2010)
iv_mine_model <- felm(as.formula(paste("d_event_mine_pw ~ lag_event_mine_pw +",
                                       controls_formula_str, iv_fe_iv_group_formula_str)),
                      ols_data, weights=ols_data$pop1564_2010)
iv_trans_model <- felm(as.formula(paste("d_event_trans_pw ~ lag_event_trans_pw +",
                                        controls_formula_str, iv_fe_iv_group_formula_str)),
                       ols_data, weights=ols_data$pop1564_2010)
iv_serv_model <- felm(as.formula(paste("d_event_serv_pw ~ lag_event_serv_pw +",
                                       controls_formula_str, iv_fe_iv_group_formula_str)),
                      ols_data, weights=ols_data$pop1564_2010)
```

Produce regression table 2

- Note: The observations and R^2 are different. Stata output is identical to table 1 which is suspicious.

```{r reg_table_2, results='asis'}
get_first_stage_f <- function(model) round(model$stage1$iv1fstat$d_export_cus_pw['F'])
first_stage_f <- sapply(list(iv_manuf_model, iv_const_model, iv_mine_model, iv_trans_model, iv_serv_model), get_first_stage_f)

stargazer(iv_manuf_model, iv_const_model, iv_mine_model, iv_trans_model, iv_serv_model, type='html',
          column.labels = c('Manufacturing', 'Construction', 'Mining', 'Transportation', 'Service'),
          dep.var.caption = "Dependent variable: Changes in CLB Events per million",
          dep.var.labels.include = FALSE, omit.stat = c('adj.rsq', 'ser'),
          digits = 4, order = c(11, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
          omit = 'dln_', omit.labels = "Additional time-t controls?",
          add.lines = list(c('First-stage F-stat', first_stage_f)))
```

### Table 3

Build IV models by cause and GDELT events. The previous regressions' dependent variables are extracted from CLB general protest event data. Here we check CLB protests with specific causes, and a different event source (GDELT).
TODO: double check data source

```{r iv_by_cause}
clb_wage_model <- felm(as.formula(paste("d_event_wage1_pw ~ lag_event_wage1_pw +",
                                        controls_formula_str, iv_fe_iv_group_formula_str)),
                       ols_data, weights=ols_data$pop1564_2010)
clb_wage_layoff_model <- felm(as.formula(paste("d_event_wage2_pw ~ lag_event_wage2_pw +",
                                               controls_formula_str, iv_fe_iv_group_formula_str)),
                              ols_data, weights=ols_data$pop1564_2010)
clb_not_wage_layoff_model <- felm(as.formula(paste("d_event_wage2a_pw ~ lag_event_wage2a_pw +",
                                                   controls_formula_str, iv_fe_iv_group_formula_str)),
                                  ols_data, weights=ols_data$pop1564_2010)
gdelt_model <- felm(as.formula(paste("d_event_GDELT_pw ~ lag_event_GDELT_pw +",
                                     controls_formula_str, iv_fe_iv_group_formula_str)),
                    ols_data, weights=ols_data$pop1564_2010)
clb_gdelt_model <- felm(as.formula(paste("d_event_pca_pw ~ lag_event_pca_pw +",
                                         controls_formula_str, iv_fe_iv_group_formula_str)),
                        ols_data, weights=ols_data$pop1564_2010)
```

Produce regression table 3. CLB & GDELT event data comes from the first principle of PCA.
Q: Why didn't GDELT data alone yield significant result?

```{r reg_table_3, results='asis'}
get_first_stage_f <- function(model) round(model$stage1$iv1fstat$d_export_cus_pw['F'])
first_stage_f <- sapply(list(clb_wage_model, clb_wage_layoff_model,
                             clb_not_wage_layoff_model, gdelt_model, clb_gdelt_model),
                        get_first_stage_f)

stargazer(clb_wage_model, clb_wage_layoff_model, clb_not_wage_layoff_model,
          gdelt_model, clb_gdelt_model, type='html',
          column.labels = c('CLB: Wage Arrears', 'CLB: Wage Arrears & Layoffs',
                            'CLB: NOT Wage Arrears & Layoffs', 'GDELT', 'CLB & GDELT'),
          dep.var.caption = "Dependent variable: Changes in Events per million",
          dep.var.labels.include = FALSE, omit.stat = c('adj.rsq', 'ser'),
          digits = 4, order = c(11, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
          omit = 'dln_', omit.labels = "Additional time-t controls?",
          add.lines = list(c('First-stage F-stat', first_stage_f)))
```

### Table 4

Inspect heterogeneous effects
- Q: What is this?
- Q: Why are college & share state employment added to iv term while investment added to dependent variables?
- Q: What do the low fisrt stage F-stats say about this table?

- TODO: check observation diff in col 5 & 6
- TODO: check first stage F stat calculation for multiple IVs

```{r iv_het}
reg_independent_and_dependent_vars <- 'd_event_pw ~ lag_event_pw + lag_fiscal_pub_security_pw'
reg_fixed_effects <-  '| prefect + province_year'
reg_formula_str <- paste(reg_independent_and_dependent_vars, reg_fixed_effects)

pub_sec_iv_lhs <- '(d_export_cus_pw|d_export_cus_pw_i_lag_fiscal_pub_security_pw'
pub_sec_iv_rhs <- '~ d_export_btkrow_pw00 + d_export_btkrow_pw00_i_lag_fiscal_pub_security_pw'
pub_sec_iv <- paste(pub_sec_iv_lhs, pub_sec_iv_rhs, ')')
pub_sec_model <- felm(as.formula(paste(reg_formula_str, pub_sec_iv, 'province', sep=' | ')),
                       ols_data, weights=ols_data$pop1564_2010)

share_state_empl_iv_lhs <- paste(pub_sec_iv_lhs, '|d_export_cus_pw_i_share_state_empl2010')
share_state_empl_iv_rhs <- paste(pub_sec_iv_rhs, '+ d_export_btkrow_pw00_i_share_state_empl2010')
share_state_empl_iv <- paste(share_state_empl_iv_lhs, share_state_empl_iv_rhs, ')')
share_state_empl_model <- felm(as.formula(paste(reg_formula_str, share_state_empl_iv,
                                                'province', sep=' | ')),
                               ols_data, weights=ols_data$pop1564_2010)

hukou_iv_lhs <- paste(share_state_empl_iv_lhs, '|d_export_cus_pw_i_share_pop_Hukou_2010')
hukou_iv_rhs <- paste(share_state_empl_iv_rhs, '+ d_export_btkrow_pw00_i_share_pop_Hukou_2010')
hukou_iv <- paste(hukou_iv_lhs, hukou_iv_rhs, ')')
hukou_model <- felm(as.formula(paste(reg_formula_str, hukou_iv, 'province', sep=' | ')),
                               ols_data, weights=ols_data$pop1564_2010)

college_iv_lhs <- paste(hukou_iv_lhs, '|d_export_cus_pw_i_share_college')
college_iv_rhs <- paste(hukou_iv_rhs, '+ d_export_btkrow_pw00_i_share_college')
college_iv <- paste(college_iv_lhs, college_iv_rhs, ')')
college_model <- felm(as.formula(paste(reg_formula_str, college_iv, 'province', sep=' | ')),
                               ols_data, weights=ols_data$pop1564_2010)

reg_formula_with_investment_str <- paste(reg_independent_and_dependent_vars,
                                         '+ lag_investment_pw', reg_fixed_effects)
investment_iv_lhs <- paste(college_iv_lhs, '|d_export_cus_pw_i_lag_investment_pw')
investment_iv_rhs <- paste(college_iv_rhs, '+ d_export_btkrow_pw00_i_lag_investment_pw')
investment_iv <- paste(investment_iv_lhs, investment_iv_rhs, ')')
investment_model <- felm(as.formula(paste(reg_formula_with_investment_str, investment_iv,
                                         'province', sep=' | ')),
                               ols_data, weights=ols_data$pop1564_2010)

reg_formula_with_investment_and_controls_str <- paste(reg_independent_and_dependent_vars,
                                                      '+ lag_investment_pw +', controls_formula_str,
                                                      reg_fixed_effects)
investment_control_model <- felm(as.formula(paste(reg_formula_with_investment_and_controls_str,
                                         investment_iv, 'province', sep=' | ')),
                        ols_data, weights=ols_data$pop1564_2010)
```

Produce regression table 4

```{r reg_table_4, results='asis'}
get_first_stage_f <- function(model) round(model$stage1$iv1fstat$d_export_cus_pw['F'])
first_stage_f <- sapply(list(pub_sec_model, share_state_empl_model, hukou_model,
                             college_model, investment_model, investment_control_model),
                        get_first_stage_f)

stargazer(pub_sec_model, share_state_empl_model, hukou_model,
          college_model, investment_model, investment_control_model,
          type='html', column.labels = rep('IV', 6),
          dep.var.labels.include = FALSE, omit.stat = c('adj.rsq', 'ser'),
          digits = 4, order = c(9, 10, 11, 12, 13, 14, 1, 2, 3),
          omit = 'dln_', omit.labels = "Additional time-t controls?",
          add.lines = list(c('First-stage F-stat', first_stage_f)))
```

### Table 5

IV regressions of export shocks on lagged "Weiwen" emphasis.
Note that the year filter is switched from 2013-2015 to 2014-2016 because the "weiwen" effect comes with a lag, which in the analysis is set to a year.

```{r prepare_weiwen_lag_data}
lagged_ols_data <- workfile_data %>%
  group_by(prefect) %>%
  mutate(lag_dln_Average_wage = lag(dln_Average_wage, order_by=year),
         lag_dln_GRP_popCSY = lag(dln_GRP_popCSY, order_by=year),
         lag_dln_college_enroll_popCSY = lag(dln_college_enroll_popCSY, order_by=year),
         lag_dln_Mobile_Tel_popCSY = lag(dln_Mobile_Tel_popCSY, order_by=year),
         lag_dln_Internet_Tel_popCSY = lag(dln_Internet_Tel_popCSY, order_by=year)) %>%
  filter(year>=2014 & year<=2016)
```

- TODO: check that `d2_export_cus_pw` of year n equals to `d_export_cus_pw` of year n-1
- Note: SVM standard errors wrongly printed in Stata table

```{r iv_weiwen}
lagged_iv_group_formula_str <- "| prefect + province_year | (d2_export_cus_pw ~ d2_export_btkrow_pw00) | province"
iv_keyword_model <- felm(as.formula(paste("d_share_keyword_word ~ lag_share_keyword_word",
                                          lagged_iv_group_formula_str)),
                       lagged_ols_data, weights=lagged_ols_data$pop1564_2010)

add_lag_prefix <- function(var) paste0('lag_', var)
lag_control_vars <- c(controls, extra_controls)
lagged_controls <- sapply(lag_control_vars, add_lag_prefix)
lagged_controls_formula_str <- paste(lagged_controls, collapse=" + ")
iv_keyword_control_model <- felm(as.formula(paste("d_share_keyword_word ~ lag_share_keyword_word",
                                                  "+", lagged_controls_formula_str,
                                                  lagged_iv_group_formula_str)),
                       lagged_ols_data, weights=lagged_ols_data$pop1564_2010)

iv_bayes_model <- felm(as.formula(paste("d_ln_para_score_w_20 ~ lag_para_score_w_20",
                                          lagged_iv_group_formula_str)),
                       lagged_ols_data, weights=lagged_ols_data$pop1564_2010)
iv_bayes_control_model <- felm(as.formula(paste("d_ln_para_score_w_20 ~ lag_para_score_w_20",
                                                "+", lagged_controls_formula_str,
                                          lagged_iv_group_formula_str)),
                       lagged_ols_data, weights=lagged_ols_data$pop1564_2010)

iv_svm_model <- felm(as.formula(paste("d_ln_para_weiwen_w_20_svm ~ lag_para_weiwen_w_20_svm",
                                          lagged_iv_group_formula_str)),
                       lagged_ols_data, weights=lagged_ols_data$pop1564_2010)
iv_svm_control_model <- felm(as.formula(paste("d_ln_para_weiwen_w_20_svm ~ lag_para_weiwen_w_20_svm",
                                              "+", lagged_controls_formula_str,
                                          lagged_iv_group_formula_str)),
                       lagged_ols_data, weights=lagged_ols_data$pop1564_2010)
```

Produce regression table 5

```{r reg_table_5, results='asis'}
get_first_stage_f <- function(model) round(model$stage1$iv1fstat$d2_export_cus_pw['F'])
first_stage_f <- sapply(list(iv_keyword_model, iv_keyword_control_model,
                             iv_bayes_model, iv_bayes_control_model,
                             iv_svm_model, iv_svm_control_model),
                        get_first_stage_f)

stargazer(iv_keyword_model, iv_keyword_control_model, iv_bayes_model,
          iv_bayes_control_model, iv_svm_model, iv_svm_control_model,
          type='html',
          column.labels = rep(c('IV: Keywords', 'IV: Naive Bayes', 'IV: SVM'), each=2),
          dep.var.labels.include = FALSE, omit.stat = c('adj.rsq', 'ser'),
          digits = 4, order = c(9, 1, 7, 8),
          omit = 'lag_dln_', omit.labels = "Additional time-t controls?",
          add.lines = list(c('First-stage F-stat', first_stage_f)))
```

### Table 6

IV regressions of export shocks on lagged fiscal expenditures.

- Q: Why chose to report log expenditure instead of share of expenditure?

```{r iv_fiscal_exp}
fiscal_pub_sec_model <- felm(as.formula(paste("d_ln_fiscal_pub_security ~ lag_ln_fiscal_pub_security",
                                              "+", lagged_controls_formula_str,
                                              lagged_iv_group_formula_str)),
                             lagged_ols_data, weights=lagged_ols_data$pop1564_2010)

fiscal_pub_serv_model <- felm(as.formula(paste("d_ln_fiscal_pub_service ~ lag_ln_fiscal_pub_service",
                                               "+", lagged_controls_formula_str,
                                               lagged_iv_group_formula_str)),
                              lagged_ols_data, weights=lagged_ols_data$pop1564_2010)

fiscal_edu_model <- felm(as.formula(paste("d_ln_fiscal_educ ~ lag_ln_fiscal_educ",
                                          "+", lagged_controls_formula_str,
                                          lagged_iv_group_formula_str)),
                         lagged_ols_data, weights=lagged_ols_data$pop1564_2010)

fiscal_social_sec_model <- felm(as.formula(paste("d_ln_fiscal_soc_security ~ lag_ln_fiscal_soc_security",
                                                 "+", lagged_controls_formula_str,
                                                 lagged_iv_group_formula_str)),
                                lagged_ols_data, weights=lagged_ols_data$pop1564_2010)

fiscal_med_model <- felm(as.formula(paste("d_ln_fiscal_medical ~ lag_ln_fiscal_medical",
                                          "+", lagged_controls_formula_str,
                                          lagged_iv_group_formula_str)),
                         lagged_ols_data, weights=lagged_ols_data$pop1564_2010)

fiscal_transport_model <- felm(as.formula(paste("d_ln_fiscal_transport ~ lag_ln_fiscal_transport",
                                                "+", lagged_controls_formula_str,
                                                lagged_iv_group_formula_str)),
                               lagged_ols_data, weights=lagged_ols_data$pop1564_2010)

fiscal_housing_model <- felm(as.formula(paste("d_ln_fiscal_housing ~ lag_ln_fiscal_housing",
                                              "+", lagged_controls_formula_str,
                                              lagged_iv_group_formula_str)),
                             lagged_ols_data, weights=lagged_ols_data$pop1564_2010)

fiscal_asset_model <- felm(as.formula(paste("d_ln_state_fund ~ lag_ln_state_fund",
                                            "+", lagged_controls_formula_str,
                                            lagged_iv_group_formula_str)),
                           lagged_ols_data, weights=lagged_ols_data$pop1564_2010)
```

Produce the top half of table 6 – Panel A: Average Effects

- Note: Column label casing inconsitency

```{r reg_table_6a, results='asis'}
get_first_stage_f <- function(model) round(model$stage1$iv1fstat$d2_export_cus_pw['F'])
first_stage_f <- sapply(list(fiscal_pub_sec_model, fiscal_pub_serv_model, fiscal_edu_model,
                             fiscal_social_sec_model, fiscal_med_model, fiscal_transport_model,
                             fiscal_housing_model, fiscal_asset_model),
                        get_first_stage_f)

stargazer(fiscal_pub_sec_model, fiscal_pub_serv_model, fiscal_edu_model,
          fiscal_social_sec_model, fiscal_med_model, fiscal_transport_model,
          fiscal_housing_model, fiscal_asset_model,
          type='html',
          column.labels = c('Public security', 'Public service', 'Education',
                            'Social security', 'Medical services', 'Transportation',
                            'Public housing', 'Fixed assets'),
          dep.var.labels.include = FALSE, omit.stat = c('adj.rsq', 'ser'),
          digits = 4, order = c(14, 1, 2, 3, 4, 5, 6, 7, 8),
          omit = 'lag_dln_', omit.labels = "Additional time-t controls?",
          add.lines = list(c('First-stage F-stat', first_stage_f)))
```

Examine heterogeneous effects

```{r fiscal_het}
rev_per_worker_12 <- workfile_data %>%
  filter(year == 2012) %>%
  mutate(fiscal_rev_tot_pw12 = fiscal_rev_tot / pop1564_2010) %>%
  select(prefect, fiscal_rev_tot_pw12)

lagged_ols_data <- lagged_ols_data %>%
  left_join(rev_per_worker_12, by="prefect") %>%
  mutate(d2_event_pw_i_d2_export_cus_pw = d2_event_pw*d2_export_cus_pw,
         d2_event_pw_i_d2_export_btkrow_pw00 = d2_event_pw*d2_export_btkrow_pw00,
         fiscal_rev_tot_pw12_i_d2_export_cus_pw = fiscal_rev_tot_pw12*d2_export_cus_pw,
         fiscal_rev_tot_pw12_i_d2_export_btkrow_pw00 = fiscal_rev_tot_pw12*d2_export_btkrow_pw00)

fixed_effect_iv_formula_str <- "+ d2_event_pw | prefect + province_year | (d2_export_cus_pw | d2_event_pw_i_d2_export_cus_pw | fiscal_rev_tot_pw12_i_d2_export_cus_pw ~ d2_export_btkrow_pw00 + d2_event_pw_i_d2_export_btkrow_pw00 + fiscal_rev_tot_pw12_i_d2_export_btkrow_pw00) | province"
control_iv_str <- paste(lagged_controls_formula_str, fixed_effect_iv_formula_str)

reg_formula_str <- "d_ln_fiscal_pub_security ~ lag_ln_fiscal_pub_security +"
het_fiscal_pub_sec_model <- felm(as.formula(paste(reg_formula_str, control_iv_str)),
                       lagged_ols_data, weights=lagged_ols_data$pop1564_2010)

reg_formula_str <- "d_ln_fiscal_pub_service ~ lag_ln_fiscal_pub_service +"
het_fiscal_pub_serv_model <- felm(as.formula(paste(reg_formula_str, control_iv_str)),
                       lagged_ols_data, weights=lagged_ols_data$pop1564_2010)

reg_formula_str <- "d_ln_fiscal_educ ~ lag_ln_fiscal_educ +"
het_fiscal_edu_model <- felm(as.formula(paste(reg_formula_str, control_iv_str)),
                       lagged_ols_data, weights=lagged_ols_data$pop1564_2010)

reg_formula_str <- "d_ln_fiscal_soc_security ~ lag_ln_fiscal_soc_security +"
het_fiscal_social_sec_model <- felm(as.formula(paste(reg_formula_str, control_iv_str)),
                       lagged_ols_data, weights=lagged_ols_data$pop1564_2010)

reg_formula_str <- "d_ln_fiscal_medical ~ lag_ln_fiscal_medical +"
het_fiscal_med_model <- felm(as.formula(paste(reg_formula_str, control_iv_str)),
                       lagged_ols_data, weights=lagged_ols_data$pop1564_2010)

reg_formula_str <- "d_ln_fiscal_transport ~ lag_ln_fiscal_transport +"
het_fiscal_transport_model <- felm(as.formula(paste(reg_formula_str, control_iv_str)),
                       lagged_ols_data, weights=lagged_ols_data$pop1564_2010)

reg_formula_str <- "d_ln_fiscal_housing ~ lag_ln_fiscal_housing +"
het_fiscal_housing_model <- felm(as.formula(paste(reg_formula_str, control_iv_str)),
                       lagged_ols_data, weights=lagged_ols_data$pop1564_2010)

reg_formula_str <- "d_ln_state_fund ~ lag_ln_state_fund +"
het_fiscal_asset_model <- felm(as.formula(paste(reg_formula_str, control_iv_str)),
                       lagged_ols_data, weights=lagged_ols_data$pop1564_2010)
```

Produce the bottom half of table 6 – Panel B: Heterogeneous Effects

- TODO: check first stage F stat calculation for multiple IVs

```{r reg_table_6b, results='asis'}
get_first_stage_f <- function(model) round(model$stage1$iv1fstat$d2_export_cus_pw['F'])
first_stage_f <- sapply(list(het_fiscal_pub_sec_model, het_fiscal_pub_serv_model,
                             het_fiscal_edu_model, het_fiscal_social_sec_model,
                             het_fiscal_med_model, het_fiscal_transport_model,
                             het_fiscal_housing_model, het_fiscal_asset_model),
                        get_first_stage_f)

stargazer(het_fiscal_pub_sec_model, het_fiscal_pub_serv_model,
          het_fiscal_edu_model, het_fiscal_social_sec_model,
          het_fiscal_med_model, het_fiscal_transport_model,
          het_fiscal_housing_model, het_fiscal_asset_model,
          type='html',
          column.labels = c('Public security', 'Public service', 'Education',
                            'Social security', 'Medical services', 'Transportation',
                            'Public housing', 'Fixed assets'),
          dep.var.labels.include = FALSE, omit.stat = c('adj.rsq', 'ser'),
          digits = 4, order = c(15, 16, 17, 14, 1, 2, 3, 4, 5, 6, 7, 8),
          omit = 'lag_dln_', omit.labels = "Additional time-t controls?",
          add.lines = list(c('First-stage F-stat', first_stage_f)))
```
