---
title: "Data Replication: The Political Economy Consequences of China's Export Slowdown"
author: "Wei Lu"
output:
  html_document:
    toc: no
  pdf_document:
    toc: no
---

```{r setup, include=FALSE}
library(readstata13)
library(tidyverse)
knitr::opts_knit$set(root.dir = '/Users/luwei/Dropbox/GDELT/')
knitr::opts_chunk$set(cache=TRUE)
```

### Variable Construction

Merge prefecture level export data with and without interim export, check correlation

```{r merge_export}
export_by_prefect_no_interim <- read.dta13('Trade Data/Customs/export_prefect_hs6_1015_noint.dta')
export_by_prefect <- read.dta13('Trade Data/Customs/export_prefect_hs6_1015.dta')
export_merged <- merge(export_by_prefect_no_interim, export_by_prefect, by=c('nbs_prefect', 'hs07_6', 'year'))
export_merged <- as.tibble(export_merged) %>%
  rename(export_no_int = export_cus.x, export = export_cus.y, hs6 = hs07_6, prefect = nbs_prefect)

export_merged
cor(export_merged['export'], export_merged['export_no_int'])
```

Merge export data with HS07 and SIC code mapping file, extract manufacturing numbers

```{r merge_sic}
hs07_sic <- read.dta13('Trade Data/Product Category/HS07_SIC.dta')
export_merged_with_sic <- merge(export_merged, hs07_sic, by.y='hs6', all.x=T)
export_manufacturing_merged <- as.tibble(export_merged_with_sic) %>%
  filter(grepl('^2|^3', sic) | hs6 %in% c("610429", "691200", "845011", "902790")) %>%
  select(prefect, year, hs6, export, export_no_int) %>%
  complete(prefect, year, hs6, fill = list(export=0, export_no_int=0))
```

Tally total export by prefecture of year 2010 and 2012 (Only used in alternative construction)

```{r total_export}
total_by_prefect_2010 <- export_manufacturing_merged %>%
  filter(year == 2010) %>%
  group_by(prefect, year) %>%
  summarize(total_exp = sum(export))

total_by_prefect_2012 <- export_manufacturing_merged %>%
  filter(year == 2012) %>%
  group_by(prefect, year) %>%
  summarize(total_exp = sum(export))
```

Check against stata numbers, tolerance = 1

```{r check_total_export}
total_exp_2010 <- as.tibble(read.dta13('total_export_cus_pref_2010_temp.dta'))
total_exp_2012 <- as.tibble(read.dta13('total_export_cus_pref_2012_temp.dta'))

merged <- merge(total_by_prefect_2010, total_exp_2010, by='prefect', all=T)
merged[is.na(merged)] <- 0 # fill missing with 0
diff_2010 <- as.tibble(merged) %>%
  mutate(diff = total_exp - total_export_cus_pref_2010 * 1000) %>%
  filter(abs(diff) > 1) # test against tolerance, expecting empty dataframe
diff_2010

merged <- merge(total_by_prefect_2012, total_exp_2012, by='prefect', all=T)
merged[is.na(merged)] <- 0 # fill missing with 0
diff_2012 <- as.tibble(merged) %>%
  mutate(diff = total_exp - total_export_cus_pref_2012 * 1000) %>%
  filter(abs(diff) > 1)
diff_2012
```

Load population data from 2010 and 2000 and use age 15-64 as labor data.
2010 data is used for baseline; 2000 data is used for IV.

```{r load_pop}
pop_2010 <- as.tibble(read.dta13('Controls/Demographic/demographic_structure_2010_Nov17.dta')) %>%
  rename(pop1564 = pop1564_2010) %>%
  select(prefect, pop1564)
pop_2000 <- as.tibble(read.dta13('Controls/Demographic/demographic_structure_2000_Nov17.dta')) %>%
  rename(pop1564 = pop1564_2000) %>%
  select(prefect, pop1564)
```

Calculate shocks: $ExpShock_{it} = \sum_k{\frac{\Delta X_{ikt}}{L_{i, 2010}}}$. This step takes a while to compute

```{r export_shock}
export_shocks <- export_manufacturing_merged %>%
  group_by(prefect, hs6) %>%
  mutate(export_diff = export - lag(export, order_by=year),
         export_no_int_diff = export_no_int - lag(export_no_int, order_by=year)) %>%
  group_by(prefect, year) %>%
  summarize(agg_export_shock = sum(export_diff, na.rm = T),
            agg_export_no_int_shock = sum(export_no_int_diff, na.rm = T)) %>%
  inner_join(pop_2010) %>%
  mutate(shock_usdk_per_worker = agg_export_shock / 1000 / pop1564,
         shock_no_int_usdk_per_worker = agg_export_no_int_shock / 1000 / pop1564)

export_shocks
```

Check against stata numbers

```{r check_export_shock}
export_shocks_stata <- as.tibble(read.dta13('Trade Data/export_pref_shock_Nov17.dta'))

export_shocks_pw_stata <- export_shocks_stata %>%
  select(prefect, year, d_export_cus_pw, d_export_cus_ni_pw) %>%
  filter(year > 2010)

export_shocks <- export_shocks %>%
  select(prefect, year, shock_usdk_per_worker, shock_no_int_usdk_per_worker)  %>%
  filter(year > 2010)

merged <- merge(export_shocks, export_shocks_pw_stata, by=c('prefect', 'year'), all=T)
merged[is.na(merged)] <- 0 # fill missing with 0
diff_export_shock <- as.tibble(merged) %>%
  mutate(diff_export_pw = d_export_cus_pw - shock_usdk_per_worker,
         diff_export_ni_pw = d_export_cus_ni_pw - shock_no_int_usdk_per_worker) %>%
  filter(abs(diff_export_pw) > 1 | abs(diff_export_ni_pw) > 1 ) # test against tolerance, expecting empty dataframe
diff_export_shock
```

Calculate IV: $ExpShockROW_{it} = \sum_k{\frac{X_{ik, 2010}}{\sum_i{X_{ik, 2010}}} \frac{\Delta X_{kt}^{ROW}}{L_{i, 2000}}}$
ROW to ROW product level data from UN Comtrade, note that the data is in \$1000 USD unit

```{r export_shock_row}
comtrade <- as.tibble(read.dta13('Trade Data/UNComtrade/export_hs6_Nov17.dta')) %>%
  select(year, hs07_6, ExpROW_ROW) %>%
  group_by(hs07_6) %>%
  mutate(export_row_row_diff = ExpROW_ROW - lag(ExpROW_ROW, order_by=year)) %>%
  rename(hs6 = hs07_6)

total_by_product_2010 <- export_manufacturing_merged %>%
  filter(year == 2010) %>%
  group_by(year, hs6) %>%
  summarize(total_exp = sum(export), total_exp_no_int = sum(export_no_int))

export_shocks_row <- export_manufacturing_merged %>%
  filter(year == 2010) %>%
  inner_join(total_by_product_2010, by=c('year', 'hs6')) %>%
  inner_join(comtrade, by='hs6') %>%
  rename(year = year.y) %>%
  select(-one_of('year.x')) %>% # drop the year 2010 column
  mutate(prefect_exp_scaled_shock = export * export_row_row_diff / total_exp,
         prefect_exp_scaled_shock_no_int = export_no_int * export_row_row_diff / total_exp_no_int) %>%
  group_by(prefect, year) %>%
  summarize(agg_export_shock = sum(prefect_exp_scaled_shock, na.rm = T),
            agg_export_no_int_shock = sum(prefect_exp_scaled_shock_no_int, na.rm = T)) %>%
  inner_join(pop_2000) %>%
  mutate(shock_usdk_per_worker = agg_export_shock / pop1564,
         shock_no_int_usdk_per_worker = agg_export_no_int_shock / pop1564)
```

Check against stata numbers

```{r check_export_shock_row}
export_shocks_row_pw_stata <- export_shocks_stata %>%
  select(prefect, year, d_export_btkrow_pw00, d_export_btkrow_ni_pw00) %>%
  filter(year > 2010)

export_shocks_row <- export_shocks_row %>%
  select(prefect, year, shock_usdk_per_worker, shock_no_int_usdk_per_worker)  %>%
  filter(year > 2010)

merged <- merge(export_shocks_row, export_shocks_row_pw_stata, by=c('prefect', 'year'), all=T)
merged[is.na(merged)] <- 0 # fill missing with 0
diff_export_shock <- as.tibble(merged) %>%
  mutate(diff_export_pw = d_export_btkrow_pw00 - shock_usdk_per_worker,
         diff_export_ni_pw = d_export_btkrow_ni_pw00 - shock_no_int_usdk_per_worker) %>%
  filter(abs(diff_export_pw) > 1 | abs(diff_export_ni_pw) > 1 ) # test against tolerance, expecting empty dataframe
diff_export_shock
```

