---
title: "[Regression Replication]: The Political Economy Consequences of China’s Export Slowdown"
author: "Wei Lu"
output:
  html_document:
    toc: TRUE
---

```{r setup, include=FALSE}
library(readstata13)
library(tidyverse)
library(lfe)
library(stargazer)
knitr::opts_knit$set(root.dir = '/Users/luwei/Dropbox/GDELT/')
knitr::opts_chunk$set(cache=TRUE)
```

### Panel Regression

Model: $\Delta(Events/L)_{it} = \beta_0(Events/L)_{i, t-1} + \beta ExpShock_{it} + \beta_x X_{it} + D_{prov, t} + D_i + \epsilon_{it}$

Where $X_{it}$ represent additional control variables.

Note that we have verified the stata numbers above, so here we use merged data from stata for regressions directly.

```{r ols}
workfile_data <- as.tibble(read.dta13('CCL_workfile_May29.dta'))
ols_data <- workfile_data %>%
  filter(year>=2013 & year<=2015) %>%
  mutate(prefect_dummy = as.factor(prefect), province_year_dummy = as.factor(province_year), province_dummy = as.factor(province)) %>%
  select(d_event_pw, lag_event_pw, d_export_cus_pw, d_export_btkchn_pw00, d_export_btkrow_pw00,
         prefect_dummy, province_year_dummy, province_dummy, prefect, province_year, province,
         pop1564_2010,
         # control variables
         dln_Average_wage, dln_GRP_popCSY, dln_college_enroll_popCSY,
         dln_Mobile_Tel_popCSY, dln_Internet_Tel_popCSY,
         # by sector event data
         d_event_manuf_pw, lag_event_manuf_pw, d_event_const_pw, lag_event_const_pw,
         d_event_mine_pw, lag_event_mine_pw, d_event_trans_pw, lag_event_trans_pw,
         d_event_serv_pw, lag_event_serv_pw,
         # by cause & gdelt
         d_event_wage1_pw, lag_event_wage1_pw, d_event_wage2_pw, lag_event_wage2_pw,
         d_event_wage2a_pw, lag_event_wage2a_pw, d_event_GDELT_pw, lag_event_GDELT_pw,
         d_event_pca_pw, lag_event_pca_pw
         )

# lm produces the correct point estimates, but standard errors are off
# Stata's aweights = R's weights in linear regression: https://rstudio-pubs-static.s3.amazonaws.com/279455_1ca98bc2ce5f45ed9ea20a647ef0c4b1.html#analytics_weights_=_glm_weights_param
ols_model_lm <- lm(d_event_pw ~ lag_event_pw + d_export_cus_pw  + prefect_dummy + province_year_dummy, data = ols_data, weights=pop1564_2010)
ols_model_lm$coefficients[1:3]

ols_model <- felm(d_event_pw ~ lag_event_pw + d_export_cus_pw  | prefect + province_year | 0 | province, ols_data, weights=ols_data$pop1564_2010)
```

Build IV models

```{r iv}
iv_fe_iv_group_formula_str <- "| prefect + province_year | (d_export_cus_pw ~ d_export_btkrow_pw00) | province"
row_iv_model <- felm(as.formula(paste("d_event_pw ~ lag_event_pw", iv_fe_iv_group_formula_str)), ols_data, weights=ols_data$pop1564_2010)

controls <- c("dln_Average_wage", "dln_GRP_popCSY", "dln_college_enroll_popCSY")
extra_controls <- c("dln_Mobile_Tel_popCSY", "dln_Internet_Tel_popCSY")
iv_control1_formula_str <- paste("d_event_pw ~ lag_event_pw", paste(controls, collapse=" + "), sep=" + ")
row_iv_control1_model <- felm(as.formula(paste(iv_control1_formula_str, iv_fe_iv_group_formula_str)), ols_data, weights=ols_data$pop1564_2010)

iv_control2_formula_str <- paste(iv_control1_formula_str, paste(extra_controls, collapse=" + "), sep=" + ")
row_iv_control2_model <- felm(as.formula(paste(iv_control2_formula_str, iv_fe_iv_group_formula_str)), ols_data, weights=ols_data$pop1564_2010)

rf_control2_formula_str <- paste(iv_control2_formula_str, "d_export_btkrow_pw00", sep=" + ")
rf_fe_group_formula_str <- "| prefect + province_year | 0 | province"
rf_control2_model <- felm(as.formula(paste(rf_control2_formula_str, rf_fe_group_formula_str)), ols_data, weights=ols_data$pop1564_2010)
```

Produce regression table 1

```{r reg_table_1, results='asis'}
get_first_stage_f <- function(model) round(model$stage1$iv1fstat$d_export_cus_pw['F'])
first_stage_f <- sapply(list(row_iv_model, row_iv_control1_model, row_iv_control2_model), get_first_stage_f)

stargazer(ols_model, row_iv_model, row_iv_control1_model, row_iv_control2_model, rf_control2_model, type='html',
          column.labels = c('OLS', 'IV', 'IV', 'IV', 'RF'),
          dep.var.caption = "Dependent variable: Changes in CLB Events per million",
          dep.var.labels.include = FALSE, omit.stat = c('adj.rsq'),
          digits = 4, order = c(2, 8, 9, 1, 3, 4, 5, 6, 7),
          add.lines = list(c('First-stage F-stat', '', first_stage_f)))
```

Build IV models by sector

```{r iv_by_sector}
controls_formula_str <- paste(paste(controls, collapse=" + "), paste(extra_controls, collapse=" + "), sep=" + ")
iv_manuf_model <- felm(as.formula(paste("d_event_manuf_pw ~ lag_event_manuf_pw +", controls_formula_str, iv_fe_iv_group_formula_str)), ols_data, weights=ols_data$pop1564_2010)
iv_const_model <- felm(as.formula(paste("d_event_const_pw ~ lag_event_const_pw +", controls_formula_str, iv_fe_iv_group_formula_str)), ols_data, weights=ols_data$pop1564_2010)
iv_mine_model <- felm(as.formula(paste("d_event_mine_pw ~ lag_event_mine_pw +", controls_formula_str, iv_fe_iv_group_formula_str)), ols_data, weights=ols_data$pop1564_2010)
iv_trans_model <- felm(as.formula(paste("d_event_trans_pw ~ lag_event_trans_pw +", controls_formula_str, iv_fe_iv_group_formula_str)), ols_data, weights=ols_data$pop1564_2010)
iv_serv_model <- felm(as.formula(paste("d_event_serv_pw ~ lag_event_serv_pw +", controls_formula_str, iv_fe_iv_group_formula_str)), ols_data, weights=ols_data$pop1564_2010)
```

Produce regression table 2. The observations and R^2 are different. Stata output is identical to table 1 which is suspicious.

```{r reg_table_2, results='asis'}
get_first_stage_f <- function(model) round(model$stage1$iv1fstat$d_export_cus_pw['F'])
first_stage_f <- sapply(list(iv_manuf_model, iv_const_model, iv_mine_model, iv_trans_model, iv_serv_model), get_first_stage_f)

stargazer(iv_manuf_model, iv_const_model, iv_mine_model, iv_trans_model, iv_serv_model, type='html',
          column.labels = c('Manufacturing', 'Construction', 'Mining', 'Transportation', 'Service'),
          dep.var.caption = "Dependent variable: Changes in CLB Events per million",
          dep.var.labels.include = FALSE, omit.stat = c('adj.rsq'),
          digits = 4, order = c(11, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
          omit = 'dln_', omit.labels = "Additional time-t controls?",
          add.lines = list(c('First-stage F-stat', first_stage_f)))
```

Build IV models by cause and GDELT events. The previous regressions' dependent variables are extracted from CLB general protest event data. Here we check CLB protests with specific causes, and a different event source (GDELT).
TODO: double check data source

```{r iv_by_cause}
clb_wage_model <- felm(as.formula(paste("d_event_wage1_pw ~ lag_event_wage1_pw +", controls_formula_str, iv_fe_iv_group_formula_str)), ols_data, weights=ols_data$pop1564_2010)
clb_wage_layoff_model <- felm(as.formula(paste("d_event_wage2_pw ~ lag_event_wage2_pw +", controls_formula_str, iv_fe_iv_group_formula_str)), ols_data, weights=ols_data$pop1564_2010)
clb_not_wage_layoff_model <- felm(as.formula(paste("d_event_wage2a_pw ~ lag_event_wage2a_pw +", controls_formula_str, iv_fe_iv_group_formula_str)), ols_data, weights=ols_data$pop1564_2010)
gdelt_model <- felm(as.formula(paste("d_event_GDELT_pw ~ lag_event_GDELT_pw +", controls_formula_str, iv_fe_iv_group_formula_str)), ols_data, weights=ols_data$pop1564_2010)
clb_gdelt_model <- felm(as.formula(paste("d_event_pca_pw ~ lag_event_pca_pw +", controls_formula_str, iv_fe_iv_group_formula_str)), ols_data, weights=ols_data$pop1564_2010)
```

Produce regression table 3.

```{r reg_table_3, results='asis'}
get_first_stage_f <- function(model) round(model$stage1$iv1fstat$d_export_cus_pw['F'])
first_stage_f <- sapply(list(clb_wage_model, clb_wage_layoff_model, clb_not_wage_layoff_model, gdelt_model, clb_gdelt_model), get_first_stage_f)

stargazer(clb_wage_model, clb_wage_layoff_model, clb_not_wage_layoff_model, gdelt_model, clb_gdelt_model,
          type='html',
          column.labels = c('CLB: Wage Arrears', 'CLB: Wage Arrears & Layoffs',
                            'CLB: NOT Wage Arrears & Layoffs', 'GDELT', 'CLB & GDELT'),
          dep.var.caption = "Dependent variable: Changes in Events per million",
          dep.var.labels.include = FALSE, omit.stat = c('adj.rsq'),
          digits = 4, order = c(11, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
          omit = 'dln_', omit.labels = "Additional time-t controls?",
          add.lines = list(c('First-stage F-stat', first_stage_f)))
```
